\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Evaluating Currency Exposures and Hedging Strategies Amidst Global Economic Challenges:\\
A Six-Month Outlook for ABC Firm}

\author{Krish Gupta s3865829}   

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{placeins}

\let\Oldsubsection\subsection
\renewcommand{\subsection}{\FloatBarrier\Oldsubsection}

\let\Oldsubsubsection\subsubsection
\renewcommand{\subsubsection}{\FloatBarrier\Oldsubsubsection}


\begin{document}
\maketitle

\tableofcontents
\pagebreak

\section*{Executive Summary}
\addcontentsline{toc}{section}{Executive Summary}

\section*{Economic and Geopolitical Exposure Impact on Firm ABC}
\addcontentsline{toc}{section}{Economic and Geopolitical Exposure Impact on Firm ABC}
Firm ABC, a prominent agricultural machinery manufacturer based in Australia, is strategically placed in the global market with its extensive network of suppliers from countries like Japan, Germany, and the USA, and its diversified clientele across New Zealand, Canada, the UK, and Italy. However, the current global economic climate, especially the rising trend of high inflation rates, widespread interest rate hikes, and the volatile geopolitical landscape, brings the firm multifaceted challenges and exposures.\\

\noindent Firstly, the global-wide high inflation rates directly affect Firm ABC's operations. With increased costs of raw materials stated in ABARES 2023 Australian Agriculture Snapshot, vital for the manufacturing process, can be exacerbated by the firm's international supply chain, particularly given its payment obligations in multiple currencies, like JPY, EUR and USD, over the upcoming months. The company's potential inability to pass these augmented production costs to the end consumer could erode its profit margins. Furthermore, as inflation erodes consumers' purchasing power, this could lead to subdued demand for Firm ABC's machinery, especially in countries with more pronounced inflation (RBA 2023). The inflation disparity between Australia and its trade partners can dent the firm's export competitiveness. Coupled with business uncertainty and high inflation rates can disrupt the company's long-term growth strategy, affecting investment decisions and potential expansions.\\

\noindent Global-wide interest rate hikes introduce another layer of complexity to Firm ABC's financial management. With two significant payments due in EUR to their German supplier and another substantial payment in USD to their US supplier, the company's borrowing costs could rise. If the Australian dollar weakens in this environment, the firm's payment obligations in foreign currencies might become more expensive, impacting the firm's liquidity and overall financial health. Moreover, their 2,000,000 EUR term deposit in the UK might be affected by rate changes, influencing the return on this investment. On the consumer front, higher interest rates could deter spending on capital-intensive products like agricultural machinery, diminishing Firm ABC's sales (IBISWorld 2023). A potential appreciation of the Australian dollar due to interest rate dynamics could further hamper the firm's export competitiveness.\\

\noindent Lastly, the ever-evolving global geopolitical environment poses both risks and opportunities. The company's vast export portfolio exposes it to trade policies and potential tariffs (ACCC 2021). A sudden geopolitical event might lead to supply chain disruptions, especially concerning Firm ABC's pending payments and receivables in diverse currencies like NZD, CAD, GBP, and EUR (KPMG 2020). Unforeseen changes in trade regulations, intellectual property rights, or environmental standards could add operational challenges, while market volatility triggered by geopolitical unrest could impact consumer demand and confidence.\\

\noindent While Firm ABC enjoys a broad-based global footprint and diversified operations, it faces significant exposure to global economic dynamics and geopolitical uncertainties. The firm's multifaceted international engagements in procurement and sales necessitate proactive risk management, financial hedging, and a nimble operational strategy to navigate these challenging times.\\



\end{document}  